The Decline of US Birth Rates: Analyzing Minimum Wages, Abortion Policies, Education, and Child Support Enforcement

### 2024-02-15 paper/paper.qmd
fixed

author: 
  - Rayan Awad Alim
  - Maria Mangru
  - Isha Juneja
thanks: "Code and data are available at: https://github.com/RayanAlim/Birth_Rate_Analysis"
date: today
date-format: long
abstract: "Melissa S. Kearney, Phillip B. Levine, and Luke Pardue in their paper, 
'The Puzzle of Falling US Birth Rates since the Great Recession', analyze the 
decreasing birth rates within the US. In this paper, we repicate use their data 
and replicate their results of their study. While they focused on examining 
birth rates by demographics, we focus on minimum wages, education, abortion 
poilicy, and child support enforcement. The importance of our research is that 
it highlights the underlying cause of why parents may not to have many children, 
which leads to a decline in birthrates."
format: pdf
number-sections: true
#bibliography: references.bib
editor: 
  markdown: 
    wrap: 72
---

@@

In this paper, we created a linear regression model to determine the
impact of abortion policy on number of birthrates. We analyzed the
affects of education on the number of birthrates by tracking the the
birthrate for each education level separately. Additionally, to gage the
impact of childcare support enforcement on the number of birthrates, we
looked at how the maximum welfare benefits, including Medicaid, affect
low-income individuals. Analyzing the wages, abortion policies,
education, and childcare support important because they give deeper
insights regarding why parents may not prefer to have many children and
therefore may cause a decline in birthrates. The paper is structured to
include the data, results, and the discussion that include our analysis.
Although the code used in the original paper is Strata, we use R[@citeR]
to replicate some of its graphs, as well as to conduct analysis of our
own.

@@

# References
Grundy E, Murphy M. Demography and public health. In: Detels R, Gulliford M, Karim QA, Tan CC, editors. Oxford textbook of global public health. 6th ed. Oxford, England: Oxford University Press, 718–35. 2015.

>>>>

author: 
  - Rayan Awad Alim
  - Maria Mangru
  - Isha Juneja
thanks: "Code and data are available at: https://github.com/RayanAlim/Birth_Rate_Analysis"
date: today
date-format: long
abstract: "Melissa S. Kearney, Phillip B. Levine, and Luke Pardue in their paper, 
'The Puzzle of Falling US Birth Rates since the Great Recession', analyze the 
decreasing birth rates within the US. In this paper, we repicate use their data 
and replicate their results of their study. While they focused on examining 
birth rates by demographics, we focus on minimum wages, education, abortion 
poilicy, and child support enforcement. The importance of our research is that 
it highlights the underlying cause of why parents may not to have many children, 
which leads to a decline in birthrates."
format: pdf
number-sections: true
bibliography: references.bib
editor: 
  markdown: 
    wrap: 72
---

@@

In this paper, we created a linear regression model to determine the
impact of abortion policy on number of birthrates. We analyzed the
affects of education on the number of birthrates by tracking the the
birthrate for each education level separately. Additionally, to gage the
impact of childcare support enforcement on the number of birthrates, we
looked at how the maximum welfare benefits, including Medicaid, affect
low-income individuals. Analyzing the wages, abortion policies,
education, and childcare support important because they give deeper
insights regarding why parents may not prefer to have many children and
therefore may cause a decline in birthrates. The paper is structured to
include the data, results, and the discussion that include our analysis.
Although the code used in the original paper is Strata, we use R[@citeR], and other data exploration libraries[@knitr], [@rDplyr], [@rReadr], [@rGgplot2], [@rTidyverse] 
to replicate some of its graphs, as well as to conduct analysis of our
own.

@@

# References
